Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-08-01 literature/paper_draft.qmd
finish draft for 1st sim section

In this setting, we aim to assess the performance of MinT with NOVELIST when the size of the hierarchy becomes larger. As shown in @fig-sim-results-1, ...

>>>>

As shown in @fig-sim-results-1, the larger, more complex the hierarchy is, the better reconciliation strategies perform across 1- to 4-step-ahead forecasting horizons. The length of training set gives better-fitted models, but does not affect the relative improvements of the methods over the base forecasts, except MinT with sample covariance (mint_sample). This is evidence that these high-dimensional covariance estimator--shrinkage and NOVELIST--successfully handle "$n \ll p$" data. However, MinT with either estimators rarely differ.

NOVELIST has the flexibility to minimise the effects of weak correlations and retain the stronger ones, as opposed to shrinkage. Thus, this prompts us to give NOVELIST a scenario where the covariance matrix has entries that is noisy while they are, in fact, zeros. We simulate this via a sparse covariance structure of the data generating process for bottom series, which will be discussed next.
